\documentclass[10pt]{amsart}
\usepackage{paralist, xcolor, tikz}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\newcommand{\jbl}[1]{{\color{orange} Comment from Professor Lewis: #1}} % to make my life easier when commenting later
\newcommand{\RR}{\mathbb{R}}
% tinker with these to get something you like the look of: control paragraph indentation and spacing
\setlength{\parindent}{0em}
\setlength{\parskip}{.25em}
\pagestyle{empty}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}
\usepackage{xcolor}

\newtheorem*{proposition}{Proposition}
\begin{document}

%paralist indentation
\setdefaultleftmargin{0em}{3em}{}{}{}{}


\title{Open Guidelines Software Engineering Volunteer Project}
\maketitle
\thispagestyle{empty}
Open Guidelines is an initiative focused on providing free, unrestricted access to clinical guidelines used by healthcare professionals in hospitals.

We are seeking support to modernize and restore a clinical guidelines mobile application used by doctors, nurses, midwives, and biomedical technicians in Malawi. The application provides access to neonatal and newborn care guidelines developed in partnership with Malawi’s Ministry of Health and NEST 360° (Rice University and Malawi College of Medicine), supporting healthcare workers in the management of neonatal morbidity and mortality and the use of essential newborn care technologies.

The original application has become outdated and is no longer available on the Apple App Store or Google Play Store due to device incompatibilities. Despite this, clinicians in Malawi continue to request access to the resource. The project involves rebuilding, updating, or maintaining the application to ensure modern device compatibility, accessibility, and continued dissemination of critical clinical guidance for maternal, newborn, and child health care across Malawi. Any contribution toward redevelopment, technical implementation, or long-term sustainability would have a meaningful impact.

\section{What You Will Do}
\begin{itemize}
\item Migrate the existing codebase from Kotlin to React Native
\item Redeploy the application on the iOS app store and Android app store
\item Engineer a Retrieval Augmented Generation (RAG) chatbot integration to the app
\item Create a CI/CD pipelines on the GitHub and create an accurate source of documentation.
\item Sit in on calls with the customer 
\end{itemize}

Overall, it's a learning opportunity for anyone who wants to come onboard. There's no prerequistes to working on this project. Knowing how tough the job market is, I would like to help others out.

\section{Time Commitment}
You can commit as little or as much time as you would like to the project. It is a volunteer effort so all efforts towards the cause is greatly appreciated. All meetings are optional.
\end{document}

